Field-informed Reinforcement Learning for Learning Large Scale Collective Tasks

### 2023-05-03 paper.tex
chore: remove section written twice

In this paper, we propose a novel approach combining aggregate computing~\cite{Beal2015Computer} with Graph Neural Networks~\cite{Zhou2020AIOpen} to focus on the relevant areas. We further combine this with reinforcement learning techniques to respond to changing conditions in the environment.
%Specifically, we will show... \lukas{more info...}
Specifically, 
 our approach utilizes aggregate computing to disseminate information by manipulating a computational field, 
 which is a distributed data structure that maps devices to information. 
 This field functions as a dynamic environment in which information is continuously updated and diffused throughout the system. 
 By leveraging this layer, we can build collective distributed intelligence using \ac{GNN},
  which uses the information in the field to determine the best action for a given task.
\ga{first draft, need a refinement}
The remainder of this paper is structured as follows. First, we introduce the relevant background and problem formulation in \Cref{sec:background}. Afterwards, we introduce our approach in Section~\Cref{sec:approach}. Section~\Cref{sec:eval} outlines the performed experiments and discusses the obtained results. Finally, we will present our conclusions in Section~\Cref{sec:conclusion}.

>>>>

In this paper, we propose a novel approach combining aggregate computing~\cite{Beal2015Computer} with Graph Neural Networks~\cite{Zhou2020AIOpen} to focus on the relevant areas. We further combine this with reinforcement learning techniques to respond to changing conditions in the environment.
%Specifically, we will show... \lukas{more info...}
Specifically, 
 our approach utilizes aggregate computing to disseminate information by manipulating a computational field, 
 which is a distributed data structure that maps devices to information. 
 This field functions as a dynamic environment in which information is continuously updated and diffused throughout the system. 
 By leveraging this layer, we can build collective distributed intelligence using \ac{GNN},
  which uses the information in the field to determine the best action for a given task.
\ga{first draft, need a refinement}
The remainder of this paper is structured as follows. First, we introduce the relevant background and problem formulation in \Cref{sec:background}. Afterwards, we introduce our approach in \Cref{sec:approach}. \Cref{sec:eval} outlines the performed experiments and discusses the obtained results. Finally, we will present our conclusions in \Cref{sec:conclusion}.
